\appendix
\chapter{Review Process}
\section{Phases of Review}
\paragraph{} Project was evaluated at phases with major checkpoints as follows :\\

\textbf {\underline{Pre-Review :  \textit{Defining Problem Statement and Feasibility analysis Review}}}
\begin{enumerate}
\item Understanding of the problem statement.  
\item Technical understanding of domain. 
\item Identification of differentiating features.
\item Feasibility of conversion to product or paper.
\end{enumerate}

\textbf {\underline{1st Review :  \textit{Literature survey and Project plan Review }}}
\begin{enumerate}
\item Clarity in understanding of the problem/project. 
\item Completion of Literature Survey. 
\item Identification of sub-blocks and their interaction.
\item Timeline for completion of project using Gantt chart.
\end{enumerate}

\textbf {\underline{2nd Review :  \textit{Module level design and Test Plan Review}}}
\begin{enumerate}
\item Detail design of each module. 
\item Integration and module test plan. 
\item Availability status of required Hardware and Software components.
\item 20\% Completion of Block/Sub module implementation.
\end{enumerate}
    
\textbf {\underline{3rd Review :  \textit{Project Progress Review}}}
\begin{enumerate}
\item Adherences to project plan.
\item Completion of module interaction interface design.
\item 50\% Module level implementation.
\item Demonstration of completed modules using primitive interfaces 
\end{enumerate}

\textbf {\underline{4th Review :  \textit{Project Progress and Finishing plan Review}}}
\begin{enumerate}
\item 70\% Module level implementation 
\item Presentation of completed test data as per test plan.
\item Packaging plan.
\item Final demonstration plan.
\end{enumerate}

\textbf {\underline{5th Review :  \textit{Module completion and Integration Review}}}
\begin{enumerate}
\item 100\% Module implementation.
\item Completion of Integration.
\item Presentation of test data as per test plan.
\item Adherences to project plan.
\end{enumerate}

\textbf {\underline{6th Review :  \textit{Demonstration Review }}}
\begin{enumerate}
\item Quality of packaged full demo presentation. 
\item Integration test data as per test plan.
\item Quality of documentation made across project.
\item Group presentation / communication skill. 
\end{enumerate}



